INTELLIGENT SYSTEMS

### 2021-04-03 paper_4.tex
finish 4.4.3

>>>>

\subsubsection{A State of the Art Camera Independent Method}
The following section presents a competitive method \cite{0807099125} that can beat the 
performance of \cite{0807099122}. Also in this new method there is an even deeper CNN 
that uses a set of images on which a CCM pre-processing phase has already 
been applied. The comparisons of the results obtained by \cite{0807099122} and by \cite{0807099125} in 
all the techniques proposed in \ref{recommend} where it can be seen that all the error 
rates of \cite{0807099125} are smaller than those of \cite{0807099122} and therefore the model is able to 
reach the camera/scene-independece more easily.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper4/25tech1.png}
    \centering
    \caption{Camera Independence of \cite{0807099122} with CCM on $ 1^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}
    \label{fig:25t1}
    \begin{minipage}[t]{.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{images/paper4/25tech2.png}
        \caption{\small Camera Independence of \cite{0807099122} on $ 2^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
    \end{minipage}
    \hfill
    \begin{minipage}{.45\linewidth}
        \centering
        \includegraphics[width=\linewidth]{images/paper4/25tech3.png}
        \caption{\small Camera Independence of \cite{0807099122} on $ 3^{nd} $ thecnique. Mean, Median and Maximum RAE of CNN.}\label{fig:1}
    \end{minipage}  
    \label{fig:1-2}
\end{figure}

\subsection{CONCLUSION}
